\documentclass{sig-alternate}

\usepackage{graphicx}


\usepackage{url}
\usepackage{hyperref}
\hypersetup{breaklinks}

\begin{document}
\title{Adaptive and Heterogeneous Hadoop MapReduce}
\author{Aaron Burkhart, Ross Nordstrom\\
        University of Colorado - Colorado Springs\\
        1420 Austin Bluffs Pkwy,\\
        Colorado Springs, CO 80918\\
        \texttt{\{aburkhar,rnordstr\}@uccs.edu}
       }
\date{April 2014}

\maketitle

\begin{abstract}
Hadoop is a commonly used Apache implementation of MapReduce, a technique for
parallel processing in distributed systems. One weakness of Hadoop is it does
not compute input splits or assign tasks based on the computers' computational capabilities.
This causes an execution time skew between nodes, leaving high performing nodes waiting
for low performing nodes to finish. This skew can also be caused by interference from
third party VMs running on the same hardware as nodes in the Hadoop cluster. By scaling
how much work is sent to a given computer based on its capabilities, we can
redce the difference in task completion time across the system, and thus improve
the overall performance of Hadoop. We call such a system -- with computers of
varying capabilities -- a heterogeneous environment. This research aims to develop
a task scheduling and assignment algorithm for Hadoop MapReduce that is sensitive
to both the hardware configurations of the nodes in the cluster and interference
from other non-cluster nodes running on the same hardware as cluster node.
\end{abstract}

\category{C.2.4}{Performance}{Cloud computing}
\terms{Performance, Design}
\keywords{Hadoop, MapReduce, Heterogeneous, Configuration, Cloud}

\section{Introduction}
Hadoop MapReduce is well-liked for its ability to dispatch tasks across workers
in a datacenter. Hypothetically, if the work is split up into equal parts and dispatched
efficiently across similar nodes, the system will work well. In reality, datacenters today are being
updated continuously with new hardware, while old hardware lingers in the datacenter.
Some customers are willing to pay more for high performing nodes, while others prioritize cost over
performance. This diversity in customer needs contributes to diversity in datacenter hardware.
Additionally, most consumers of datacenters are not the owners. Take Amazon EC2
or Windows Azure, for example. Companies maintain datacenters and sell access to
it as a service.

Because modern datacenters are so frequently consumed as a service, the consumer
has little control over what hardware to which they will have access. Even if the
consumer had full control over which hardware they accessed, it is costly and
inefficient to maintain a datacenter full of machines with identical hardware.
Additionally, creating an algorithm to deploy a given MapReduce job across only
identical machines would be difficult.

Another issue with modern datacenters, is that the hardware is shared between users.
The user deploying a Hadoop cluster usually won't have control over which physical
machines their VMs will be deployed to and there may very well be other users with
VMs sharing and competing for physical hardware resources. This can cause performance
degradation for some of the nodes in your cluster, further imbalancing execution time.
This is true for both homogeneous and heterogeneous clusters.

Rather than fight the structure of datacenters, adapting Hadoop to the environment
in which it is deployed would allow for optimal MapReduce performance in arbitrary
environments. This is especially important when deploying Hadoop using an IaaS
(infrastructure as a service).

Our research aims to modify Hadoop v1.2.1 to adaptively vary the sizes of the input
splits and dispatch MapReduce tasks based on both the workers' computational power
and scheduling status. In this paper, we discuss the existing implementation of Hadoop
and elaborate the issues it has when executing on heterogeneous environments. We then
describe our solution in more detail and evaluate our resulting implementation. Finally
we suggest directions for future work and improvements to our progress.

\input{motivation}
\input{relatedwork}
\input{proposeddesign}
\input{implementation}
\input{futurework}
\input{conclusion}

\bibliography{citations}{}
\bibliographystyle{plain}

\end{document}

